\documentclass[10pt,a4paper,withhyper]{altacv}


\geometry{left=1cm,right=1cm,top=0.7cm,bottom=0.7cm,columnsep=1.2cm,papersize={25cm, 56cm}}



\usepackage{paracol}



\iftutex
  \setmainfont{Lato}
\else
  \usepackage[default]{lato}
\fi


\definecolor{VividPurple}{HTML}{3E0097}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{666666}
\colorlet{heading}{VividPurple}
\colorlet{headingrule}{VividPurple}
\colorlet{accent}{VividPurple}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}

\renewcommand{\cvItemMarker}{{\small\textbullet}}
\renewcommand{\cvRatingMarker}{\faCircle}


% If your CV/résumé is in a language other than English,
% then you probably want to change these so that when you
% copy-paste from the PDF or run pdftotext, the location
% and date marker icons for \cvevent will paste as correct
% translations. For example Spanish:
% \renewcommand{\locationname}{Ubicación}
% \renewcommand{\datename}{Fecha}


\input{pubs-num}


\addbibresource{sample.bib}

\begin{document}
\name{SLIMANI YASSINE}
\tagline{Software Engineer}

\personalinfo{
  \email{slimaniiyassine@gmail.com}
  \phone{00 212 6 67 99 17 70}
  \location{Kenitra, Morocco}
  \linkedin{yassine-slimani}
  \xtwitter{@SlimaniYasssine}
  \github{/slimaniiyassine} 
\divider
}

\makecvheader

\AtBeginEnvironment{itemize}{\small}

\columnratio{0.6}

\begin{paracol}{2}
	
\cvsection{Summary}

{Experienced Mobile engineer with 8 years of expertise in native Android development (Kotlin/Java), aiming to deliver user-focused solutions with strong UX development. \newline With an analytical approach and decision-making ability, I have led 5 teams of 5 developers and simultaneously executed 3 large-scale projects delivering high-performance applications in telecommunications, banking, e-commerce and healthcare.\newline Strong background in clean architecture and project delivery in Agile environments. Seeking a challenging role with growth opportunities while contributing to the development of high-quality applications.}

\cvsection{Experience}

\cvevent{Senior Android Developer | Lead Android Developer | App Architect | System Architect }{Bell Canada (via Cnexia)}{Sep 2022 -- Ongoing}{Rabat, Morocco}

\textbf{Promoted to Lead Android Developer.}
\newline
\textbf{Promoted to App Architect.}
\newline
\textbf{Promoted to System Architect.}
\newline

\textbf{Missions:}
\begin{itemize}
\addtolength{\itemindent}{0.1cm}
\item Analyzed functional and technical requirements to define application architecture.
\item Supported technical teams in implementing architectural choices.
\item Supervised code reviews, automated tests, and pipelines.
\item Reviewed merge requests for a better quality code.
\item Led the Android Matrix team, coordinating requirements, development and delivery.
\item Managed technical designs and solutions architecture.
\item Conducted client’s demos.
\item Migrated a full library to Jetpack Compose.
\item Implemented accessibility features and integrated OneTrust SDK.
\item Maintained code quality and estimated features.
\item Improved code coverage to match the new quality gates.
\item Onboarding and mentoring of new Android developers.
\item Assured technological watch to anticipate and integrate relevant developments.
\end{itemize}

\textbf{Technologies:}

\begin{itemize}
\addtolength{\itemindent}{0.1cm}
\item Kotlin/MVVM/Compose/Coroutines.
\item Atlassian Jira, Atlassian Confluence, Github, Jenkins, SonarQube.

\end{itemize}

\textbf{Applications:}

\href{https://play.google.com/store/apps/details?id=ca.bell.selfserve.mybellmobile&hl=en&gl=CA&pli=1}{\textit{Google Play MyBell (Webby Awards Winner)}}.
\newline
\href{https://play.google.com/store/apps/details?id=ca.virginmobile.myaccount.virginmobile&hl=en}{\textit{Google Play Virgin Plus My Account}}.
\newline
\href{https://play.google.com/store/apps/details?id=ca.luckymobile&hl=en}{\textit{Google Play Lucky Mobile My Account)}}.
\newline
\href{https://play.google.com/store/apps/details?id=ca.pcmobile.selfserve.mypcmobile&hl=en}{\textit{Google Play My PC mobile (Prepaid))}}.

\divider

\cvevent{Senior Android Developer | Lead Android Developer }{Nespresso (via Sqli)}{Oct 2018 - Sep 2022}{Rabat, Morocco}

\textbf{Promoted to Lead Android Developer.}
\newline

\textbf{Missions:}
\begin{itemize}
\addtolength{\itemindent}{0.1cm}
\item Secured performance optimization and security management.
\item Coordinated with product, design, backend, and QA teams.
\item Integrated Dagger in a multi-module environment.
\item Conducted technical feasibility studies and unit test implementations.
\item Delivered stable and scalable solutions across multiple releases.
\item Implemented binding adapters to enhance reusability and to improve testability.
\item Centralized different staging apps using product flavors to have one code base.
\end{itemize}

\textbf{Technologies:}
\begin{itemize}
	\addtolength{\itemindent}{0.1cm}
	\item Kotlin, MVVM, MVC, RXjava/RxKotlin, Room Database.
	\item Atlassian Jira, Atlassian Confluence, Gitlab, Jenkins, SonarQube.
\end{itemize}
\textbf{Application:}

\href{https://play.google.com/store/apps/details?id=com.nespresso.activities&hl=en}{\textit{Google Play Nespresso}}.

\divider

\cvevent{Mobile Developer}{Airbus (via Sqli)}{June 2018 - Oct 2018}{Rabat, Morocco}


\textbf{Missions:}
\begin{itemize}
	\addtolength{\itemindent}{0.1cm}
	\item Delivered incremental features through agile development cycles.
	\item Participated in client requirement analysis and cost estimation.
\end{itemize}

\textbf{Technologies:}
\begin{itemize}
	\addtolength{\itemindent}{0.1cm}
	\item Ionic, html, wordpress.
\end{itemize}

\divider

\cvevent{Mobile Developer}{Merck (via Sqli) }{Dec 2017 - June 2018}{Rabat, Morocco}

\textbf{Missions:}

\begin{itemize}
\addtolength{\itemindent}{0.1cm}
\item Participated in client demos, task estimations and bug resolution.
\item Developed new features and optimized performance.

\end{itemize}

\textbf{Technologies:}

\begin{itemize}
	\addtolength{\itemindent}{0.1cm}
	\item React native, redux, fastlane.
	
\end{itemize}
\divider

\cvevent{Mobile Developer}{BNP Paribas (via Sqli) }{Sep 2017 - Dec 2017}{Rabat, Morocco}
\textbf{Missions:}

\begin{itemize}
	\addtolength{\itemindent}{0.1cm}
	\item Worked on feature development and bug fixing.
\end{itemize}

\textbf{Technologies:}	
\begin{itemize}
	\addtolength{\itemindent}{0.1cm}
	\item Ionic.
	
\end{itemize}
\divider

\cvevent{Mobile Developer}{Murprotec (via Sqli) }{May 2017 - Sep 2017}{Rabat, Morocco}

\textbf{Missions:}

\begin{itemize}
	\addtolength{\itemindent}{0.1cm}
	\item Conducted feasibility analysis, managed evolution requests, and presented results during client demo sessions.
\end{itemize}

	\textbf{Technologies:}	
\begin{itemize}
	\addtolength{\itemindent}{0.1cm}
	\item Android, Java.
	
\end{itemize}

\divider

\cvevent{Mobile Developer}{Adrea mutuelle (via Sqli) }{March 2017 - May 2017}{Rabat, Morocco}

\textbf{Missions:}

\begin{itemize}
	\addtolength{\itemindent}{0.1cm}
	\item Focused on bug fixing and application maintenance.
\end{itemize}
	\textbf{Technologies:}	
\begin{itemize}
	\addtolength{\itemindent}{0.1cm}
	\item Ionic.
	\item Jira.
\end{itemize}

%\cvsection{A Day of My Life}

% Adapted from @Jake's answer from http://tex.stackexchange.com/a/82729/226
% \wheelchart{outer radius}{inner radius}{
% comma-separated list of value/text width/color/detail}
% Some ad-hoc tweaking to adjust the labels so that they don't overlap
%\hspace*{-1em}  %% quick hack to move the wheelchart a bit left
%\wheelchart{1.5cm}{0.5cm}{%
  %10/13em/accent!30/Sleeping \& dreaming about work,
  %25/9em/accent!60/Public resolving issues with Yahoo!\ investors,
  %5/11em/accent!10/\footnotesize\\[1ex]New York \& San Francisco Ballet Jawbone board member,
  %20/11em/accent!40/Spending time with family,
  %5/8em/accent!20/\footnotesize Business development for Yahoo!\ after the Verizon acquisition,
  %30/9em/accent/Showing Yahoo!\ \mbox{employees} that their work has meaning,
  %5/8em/accent!20/Baking cupcakes
%}

% use ONLY \newpage if you want to force a page break for
% ONLY the currentc column


%% Switch to the right column. This will now automatically move to the second
%% page if the content is too long.
\switchcolumn

\cvsection{Skills}
%%\begin{quote}
%%``If you don't have any shadows, you're not standing in the light.''
%%\end{quote}

\begin{itemize}
	\item Leadership and team management.
	\item Communication and autonomy.
	\item Management of multiple simultaneous projects.
	\item Strategic thinking and adaptability.
	\item Decision-making and multitasking.
	\item Time and risk management.
	\item Cross-functional collaboration.
\end{itemize}

%\cvsection{Most Proud of}

%\cvachievement{\faTrophy}{Courage I had}{to take a sinking ship and try to make it float}

%\divider

%\cvachievement{\faHeartbeat}{Persistence \& Loyalty}{I showed despite the hard moments and my willingness to stay with Yahoo after the acquisition}

%\divider

%\cvachievement{\faChartLine}{Google's Growth}{from a hundred thousand searches per day to over a billion}

%\divider

%\cvachievement{\faFemale}{Inspiring women in tech}{Youngest CEO on Fortune's list of 50 most powerful women}

%\cvsection{Strengths}

% Don't overuse these \cvtag boxes — they're just eye-candies and not essential. If something doesn't fit on a single line, it probably works better as part of an itemized list (probably inlined itemized list), or just as a comma-separated list of strengths.

%\cvtag{Hard-working (18/24)}
%\cvtag{Persuasive}\\
%\cvtag{Motivator \& Leader}

%\divider\smallskip

%\cvtag{UX}
%\cvtag{Mobile Devices \& Applications}
%\cvtag{Product Management \& Marketing}
\cvsection{Technical stack}


\textbf{Kotlin Multiplatform/KMP}

\begin{itemize}
	\item Compose Multiplatform/Android/iOS/Desktop.
	\item Kotlin Multiplatform.
\end{itemize}
\divider

\textbf{Android}

\begin{itemize}
	\item Android Studio.
	\item Android Architecture Components/JetPack.
	\item Dagger 2/RxJava/RxKotlin/Retrofit/OkHttp.
	\item Kotlin Coroutines.
	\item Jetpack Compose/ViewBinding/DataBinding.
	\item Android Accessibility.
\end{itemize}
\divider

\textbf{Hybrid technologies}

\begin{itemize}
	\item Ionic.
	\item React Native.
\end{itemize}
\divider

\textbf{Software Architecture}

\begin{itemize}
	\item Clean Architecture.
	\item MVVM/MVI/MVP.
\end{itemize}
\divider

\textbf{Principle}

\begin{itemize}
	\item Clean Code/SOLID.
	\item Object Oriented Programming.
	\item Reactive Programming.
	\item Isolation/Reproducibility.
\end{itemize}
\divider

\textbf{Design Patterns}

\begin{itemize}
	\item Singleton/Builder/Factory.
	\item Delegate/Visitor/Proxy/Facade/Adapter.
	\item Chain of responsibility/Strategy.
\end{itemize}
\divider

\textbf{Continuous Integration/Deployment}

\begin{itemize}
	\item Jenkins/GitLab CI/Fastlane/Docker/SonarQube.
	\item Git.
\end{itemize}
\divider

\textbf{Android test}

\begin{itemize}
	\item Junit/Mockito/Espresso/JaCoCo/Robolectric/Leak Canary.
\end{itemize}
\divider

\textbf{Android Build System}

\begin{itemize}
	\item ProGuard/DexGuard/R8.
	\item Gradle/Maven.
	\item adb/sdkmanager/avdmanager.
\end{itemize}
\divider

\textbf{Programming Language}

\begin{itemize}
	\item Kotlin/Java.
	\item Javascript/HTML.
\end{itemize}
\divider

\textbf{Analytics/Monitoring}

\begin{itemize}
	\item Firebase/Crashlytics/Adobe Analytics/Adobe Journey Optimizer.
\end{itemize}
\divider

\textbf{Database}

\begin{itemize}
	\item Room/SQLite/Oracle.
\end{itemize}
\divider

\textbf{Tools}

\begin{itemize}
	\item Jira/Confluence/Postman/Charles Proxy.
\end{itemize}
\divider

\textbf{AI}

\begin{itemize}
	\item MCP servers.
	\item Github Copilot.
	\item Gemini nano.
	\item LoRA training.
	\item Mediapipe.
		\item Googel colab.
	\item hugging face/gemma.
\end{itemize}



\cvsection{Languages}

\cvskill{English}{4.5}
\divider

\cvskill{French}{4}
\divider

\cvskill{Arabic}{5}


\cvsection{CERTIFICATIONS}

\begin{itemize}
\item \href{https://www.scrum.org/user/418540}{\textit{Professional Scrum Developer.}}
\item \href{https://drive.google.com/file/d/1NZk4r5TWXaY0Wp3Xjmo-ku7Hr-xPkmTo/view?usp=sharing}{\textit{SAFe 6 Agilist.}}
\end{itemize}
\cvsection{Education}

\cvevent{Master’s Degree\ in new technologies and Project Management.}{University of Nice Sophia Antipolis – France}{2016 - 2017}{}

\cvevent{Engineering Degree\ in Computer Science.}{Moroccan School of Engineering Sciences (EMSI)}{2012 - 2017}{}


\cvsection{Article}

\href{https://medium.com/@slimaniiyassine/a-developers-guide-to-using-gemini-with-an-mcp-server-05878c418097}{\textit{A Developer’s Guide to Using Gemini with an MCP Server}}.

%\divider

%\cvevent{B.S.\ in Symbolic Systems}{Stanford University}{Sept 1993 -- June 1997}{}


\end{paracol}

\end{document}
